---
title: "CentralDogmaGroup7"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CentralDogmaGroup7}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Link to repository

<https://github.com/rforbiodatascience24/group_7_package>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(CentralDogmaGroup7)
```

## The functions

### Function 1

Description

```{r}
#Example
```

### Function 2

Description

```{r}
#Example
```

### Function 3

Description

```{r}
#Example
```

### Function 4

Description

```{r}
#Example
```

### Function 5

The function `plot_occurrence()` is development around the central dogma, created with the intention of taking in an amino acid sequence, and outputting a plot of the occurrence of each amino acid.

It takes in a character string, splits it into individual characters, and creates a new string containing only the unique characters. Then, it counts the occurrence of each unique character, creating a data frame with the number of times each character appears. Finally, it plots the occurrence of each unique character in a bar plot.

```{r}
sequence <- paste0(sample(c("A", "C", "D", "E", "F", "G", "H",
                            "I", "K", "L", "M", "N", "P", "Q",
                            "R", "S", "T", "V", "W", "Y"),
                          1000,
                          replace = TRUE),
                   collapse = "")

plot_occurrence(sequence)

```

## Used in conjunction

```{r}

```

## Uses and considerations
